Experimentally informed site-specific substitution models deepen phylogenetic estimates of the divergence of viral lineages

### 2018-02-26 manuscript/manuscript.tex
tweaks to empirical trrees section

The results in \ref{fig:empirical_trees} show the distinct effects of modeling variation in $\omega$ and variation in the stationary state. 
The models with $\Gamma\omega$ rate variation estimated longer branches than the same base model without this variation. 
For example, in \ref{fig:empirical_trees}, the GY94+$\Gamma\omega$ model estimated longer branches than the GY94 and the ExpCM+$\Gamma
\omega$(H1 prefs) estimated longer branches than the ExpCM(H1 prefs).

The models with site-specific stationary states, the ExpCM's, estimated longer branches than the GY94 models. 
Both the ExpCM(H1 prefs) and ExpCM(H3) prefs estimated longer branches than the GY94 model. 
However, in contrast with the effect of adding $\Gamma\omega$ rate variation, the effect of site-specific stationary defined by deep mutational scanning preferences is not uniform across the entire tree. 
The effect is largest on the branches near the focal sequence of the deep mutational scan (\ref{fig:empirical_trees}). 
While the increase in length estimated by the ExpCM's has a strong local effect, the increase is in seen even in the presence of $\Gamma\omega$ rate variation. 
The ExpCM+$\Gamma\omega$ estimated longer branches than the GY94+$\Gamma\omega$. 
The site-specificity of the ExpCM's stationary state is clearly important for estimating the long branches on the HA tree.

>>>>

The results in \ref{fig:empirical_trees} show the distinct effects of modeling variation in $\omega$ and variation in the stationary state. 
For two models with the same stationary state, the model which allows $\omega$ to vary estimates longer branches. 
For example, the GY94+$\Gamma\omega$ estimates longer branches on the HA tree than the GY94 and the ExpCM+$\Gamma\omega$(H1 prefs) estimates longer branches than the ExpCM(H1 prefs).
In addition, the models with site-specific stationary states estimate longer branches than the models with a uniform stationary state given the same $\omega$ parametrization.  
Both the ExpCM(H1 prefs) and ExpCM(H3 prefs) estimate longer branches than the GY94 model.

However, in contrast to the effect of adding $\Gamma\omega$ rate variation, the effect of the site-specific stationary state defined by deep mutational scanning preferences in not uniform across the entire tree. 
The effect is largest on the branches near the focal sequence of the deep mutational scan for both the ExpCM(H1 prefs) and ExpCM (H3 prefs). 
While the ExpCM's show an increase in branch length with a strong local effect, the increase is seen even in the presence of $\Gamma\omega$ rate variation. 
The ExpCM+$\Gamma\omega$ estimates the longest branches for all of the models tested. 
These results indicate that the site-specificity of the ExpCM stationary state is important for long branch underestimation but this stationary state is not constant across the entire HA tree.
